### 2017-11-21 manuscript.rmd
silenced, moved up, outputted to pdf file -- VARS violin plot and Overview ggheatmap figure

#####SIMMAP Sex distribution
```{r sex, echo=F, message=F, warning=F, include=F}
#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim) %>% pdf("density_sex_sim")
```

#####SIMMAP Presence of palpons
```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)%>% pdf("palpons_sim")
```

@@

Posterior probabilities of states (1 Present, 0 Absent).

@@

###SIMMAP BRACTS:
```{r bracts, echo=F, message=F, warning=F}
#Simmap bracts
plotTree(ultratree, lwd = 4)
#plot(bract_sim_plot[2])
colors = c("black", "red")
names(colors) = c("Absent","Present")
bracts_sim %>% plotSimmap(lwd = 4, add = T, colors=colors) -> bract_sim_plot
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(bracts_sim)
```

Posterior probabilities of states (1 Present, 0 Absent).It is not clear whether or not the stem group of siphonophores had a pneumatophore.

@@

####Overview grid of main binary traits
```{r ggtree_bin_heatmap, echo=F, message=F, warning=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:8,12)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(4,7,1,3,6,2,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1)
```

@@

######VARS data barplot code
```{r vars_plot, echo=F, message=F, warning=F}
#Get Raw Data
raw_data = read.csv(file="character_coding/trim_siphdepths.tsv", sep = "\t")[,c(4,3,5:11)]
raw_data = raw_data[order(raw_data$ConceptName),]

#Plots for FIGURE
ggplot(parched_data, aes(x = Species, y=-Depth)) + geom_boxplot() + theme_classic()
ggplot(parched_data, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic()

ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_boxplot() + theme_classic()
ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic()

>>>>

```{r sex, echo=F, message=F, warning=F, include=F}
#Simmap SEX
#plotTree(ultratree, lwd = 4)
#colors = c("black", "red")
#names(colors) = c("Dioecious", "Monoecious")
#sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
#nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
#add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim) %>% pdf("density_sex_sim")
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)%>% pdf("palpons_sim")
```

```{r vars_plot, echo=F, message=F, warning=F, include=F}
#Get Raw Data
raw_data = read.csv(file="character_coding/trim_siphdepths.tsv", sep = "\t")[,c(4,3,5:11)]
raw_data = raw_data[order(raw_data$ConceptName),]

#ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_boxplot() + theme_classic()
ggplot(trimmed_SDdata, aes(x = Species, y=-Depth)) + geom_violin() + theme_classic() %>% pdf("trimmed_violinVars.pdf")

```{r ggtree_bin_heatmap, echo=F, message=F, warning=F, include=F}
p <- ggtree(ultratree)
p <- p + geom_tiplab(size=2.2)
f_cdata = sapply(cdata, as.factor) %>% as.data.frame %>% .[c(1,2,5:8,12)]
rownames(f_cdata) = rownames(cdata)
f_cdata = f_cdata[,c(4,7,1,3,6,2,5)]
f_cdata[match(tree$tip.label,rownames(f_cdata)),]
gheatmap(p, f_cdata, offset = 0.4, width=0.5, colnames_position = 'top', font.size = 1) %>% pdf("overview_ggheatmap_chars.pdf")
```

@@

@@

@@

@@
